### 2020-11-17 paper/draft1.tex
formatting fun

\section{Model and Definitions}
Our model will consist of $n$ forecasters s.t. $n \ge 2$ where $i \in [1,n]$ denotes the $i$th forecaster, $m$ independent events where $k \in [1,m]$ denotes the $k$th event. Each event $k \in [1,m]$ will be associated with a random variable $X_k$. $X_k = 1$ will denote that event $k$ occurred, and, likewise, $X_k = 0$ will denote event $k$ did not occur. $\forall k \in [m] \exists \theta_k$ s.t. $\theta_k$ denotes the true, unknown probability of event $k$ occurring;  $\theta_k = P(X_k = 1) = 1 - P(X_k = 0)$. We will denote each outcome drawn as $x_i \sim X_i$. For each forecaster $i$, we denote their true belief that event $k$ will occur as $\hat{\theta}_{i,k} \in (0,1)$. We then denote $y_{i,k} \in [0,1]$ as the actual report forecaster $i$ makes for event $k$. Note that $y_{i,k}$ need not equal $\hat{\theta}_{i,k}$. \\

After every event $k \in [1,m]$ has occurred, and thus each forecaster has reported $y_{i,k} \forall i f\forall k$, a mechanism will select exactly one forecaster from the set of $[n]$ as the 'best forecaster'.\\

\textbf{Definition 1: Forecaster Selection Mechanism:}\\
Some mechanism $M(y, x)$ that maps the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_k)$ to an index $w \in [1, n]$. We say that forecaster $w$ wins the competition if $M(y, x) = w$.\\

We call a forecaster selection mechanism truthful iff, for all forecasters, their probability of winning is maximized when they reports their beliefs as their forecasts.\\

\textbf{Definition 2: Truthful:}\\
$M$ is truthful iff $\forall i \in [n]$, $\forall \hat{\theta}_i$, $\forall y^{\prime}_i \neq \hat{\theta}_i$, and $\forall y_j s.t. j \neq i$,
\[ P(M( (y_1, ..., \hat \theta_i, .., y_n), x ) = i) \geq  P(M( (y_1, ..., \hat y_i, .., y_n), x ) = i)\]
\textbf{Note:} $M$ is strictly truthful if the strict inequality inequality holds.\\

Additionally, we would like our mechanism to choose the forecaster with the best predictions. We define the accuracy of a single forecaster $i$ as 1 minus the average squared loss of their forecasts compared to the true probabilities.\\

\textbf{Definition 3: Accuracy:}\\
$a_i = 1 - \frac{1}{m}\sum_{k=1}^m (y_{i, k} - \theta_k)^2$.\\

An ideal mechanism would choose forecasters with larger accuracies with higher probabilities. Let $i^* = \argmax_i a_i$ be the highest accuracy forecaster, and let $a^* = a_{i^*}$.\\

\textbf{Definition 4: Accuracy Gap:}\\
$\epsilon = a^* - \max_{i \neq i^*} a_i$ denote the accuracy gap.\\

For a given mechanism $M$ and $n$ forecasters with accuracy gap $\epsilon$, we let $m_\delta$ be the minimum number of events such that $M$ necessarily chooses $i^*$ with probability at least $1 - \delta$. Specifically, for any $m > m_\delta(M, n, \epsilon)$, $P(M(y, x) \neq i^*) \leq \delta$. $m_\delta$ gives us a measure of how many events are needed for a mechanism to stably pick the best forecaster. We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.\\

Similar to work in \cite{elf}, we will focus on using the \textbf{proper scoring rule}, the \textbf{quadratic scoring rule} in our forecaster selection mechanism.\\

\textbf{Definition 5: Proper Scoring Rule}:\\
Scoring rule, $R$ is proper if $\forall p,y \in {0,1}, E_{x~p}[R(p,x)] \ge E_{x~p}[R(y,x)]$\\

\textbf{Definition 6: Quadratic Scoring Rule}:\\
$R_q = 1 - (y - x)^2$; Where $x$ denotes the observed outcome, and $y$ denotes the report.

@@

\subsection{Truthfulness}
show simple counterexample(s?) \\
- single event favors extremes \\
- multiple events can be dominated by single untruthful event when rest are isomorphic \\

@@

Let $F_{i, k}$ be the indicator function for forecaster $i$ winning the lottery for event $k$. Then, $F_i = \sum_k F_{i, k}$ is the random variable that is the number of events forecaster $i$ wins. The proof of Theorem 8 \cite{elf} utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance. However, this is not the case, and utilizing that fact gives an improvement in the lower bound. 
\begin{theorem}[Bernstein's Inequality]
  \label{bernstein}
  Given random variables $X_i$ for $1 \leq i \leq n$ such that $0 \leq X_i \leq 1$ almost surely, let $S = \sum_i X_i$. Then,
  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } \]
\end{theorem}
\begin{theorem}
  \label{elf_bound}
    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$
    % For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
\end{theorem}
\emph{Proof:} Note that for any single event $k$, every forecaster wins with probability at best $\frac{2}{n}$, and at worst $\frac{1}{n} - \frac{1}{n(n-1)}$ (achieved when $y_i = 1$, $y_{j\neq i} = 0$, and $x_i = 1$). Since $F_{i, k}$ is just a binary random variable, it will have highest variance when it's expectation is as close to $\frac{1}{2}$ as possible. For nontrivially small $n$, this will mean its expectation is $\frac{2}{n}$ (or equivalently $P(F_{i, k} = 1) = \frac{2}{n}$), so its variance will be at most $\frac{2(n-2)}{n^2}$. So we have $\Var(F_{i, k}) \leq \frac{2(n-2)}{n^2} < \frac{2}{n}$.

@@

\begin{theorem}
  \label{elf_lower_bound}
    For $\delta < \frac{1}{2}$, $m_\delta(\elf, n, \epsilon) > n \log n$
\end{theorem}
\emph{Proof:} Pick some $\delta < \frac{1}{2}$ and consider the case where $m = n \log n$ and $\theta_k = 1$ for every event. Let $y_{1, k} = 1$ and $y_{i, k} = 0$ for every $i > 1$. Therefore, forecaster 1 always forecasts correctly and has a quadratic score $R_q(1, 1) = 1$ for each event, while everyone else is wrong and has a quadratic score of $R_q(0, 1) = 0$ for each event. Then, $a_1 = 1$, and $a_i = 0$ for $i > 1$, so we have the worst possible accuracy gap $\epsilon = 1$.

@@

\begin{theorem}
  \label{shelf_truthful}
    $\shelf$ is truthful for $m \geq 1$ events.
\end{theorem}
\emph{Proof:} For each forecaster $j \in [1, n]$ fix forcaster's report.

@@

% \subsection{Truthfulness for multiple events}
\begin{theorem}
  \label{shelf_bound}
    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$
\end{theorem}
\emph{Proof:} This proof is a slight modification of the proof of Theorem 8 in \cite{elf}.

>>>>

\section{Model and Definitions}
Our model will consist of $n$ forecasters s.t. $n \ge 2$ where $i \in [1,n]$ denotes the $i$th forecaster, $m$ independent events where $k \in [1,m]$ denotes the $k$th event. Each event $k \in [1,m]$ will be associated with a random variable $X_k$. $X_k = 1$ will denote that event $k$ occurred, and, likewise, $X_k = 0$ will denote event $k$ did not occur. $\forall k \in [m] \exists \theta_k$ s.t. $\theta_k$ denotes the true, unknown probability of event $k$ occurring;  $\theta_k = P(X_k = 1) = 1 - P(X_k = 0)$. We will denote each outcome drawn as $x_i \sim X_i$. For each forecaster $i$, we denote their true belief that event $k$ will occur as $\hat{\theta}_{i,k} \in (0,1)$. We then denote $y_{i,k} \in [0,1]$ as the actual report forecaster $i$ makes for event $k$. Note that $y_{i,k}$ need not equal $\hat{\theta}_{i,k}$.

After every event $k \in [1,m]$ has occurred, and thus each forecaster has reported $y_{i,k} \forall i f\forall k$, a mechanism will select exactly one forecaster from the set of $[n]$ as the 'best forecaster'.

\begin{definition}
  \label{mechanism}
  A \textbf{selection mechanism} $M(y, x)$ is a map from the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_m)$ to an index $w \in [1, n]$.
\end{definition}
We say that forecaster $w$ wins the competition if $M(y, x) = w$. We call a forecaster selection mechanism truthful iff, for all forecasters, their probability of winning is maximized when they reports their beliefs as their forecasts.

\begin{definition}
  \label{truthfullness}
  $M$ is \textbf{truthful} iff $\forall i \in [n]$, $\forall \hat{\theta}_i$, $\forall y^{\prime}_i \neq \hat{\theta}_i$, and $\forall y_j s.t. j \neq i$,
\[ P(M( (y_1, ..., \hat \theta_i, .., y_n), x ) = i) \geq  P(M( (y_1, ..., \hat y_i, .., y_n), x ) = i)\]
$M$ is \textbf{strictly truthful} if the strict inequality inequality holds.
\end{definition}

Additionally, we would like our mechanism to choose the forecaster with the best predictions. We define the accuracy of a single forecaster $i$ as 1 minus the average squared loss of their forecasts compared to the true probabilities.

\begin{definition}
  \label{accuracy}
  A forecaster's \textbf{accuracy} is $a_i = 1 - \frac{1}{m}\sum_{k=1}^m (y_{i, k} - \theta_k)^2$.
\end{definition}
An ideal mechanism would choose forecasters with larger accuracies with higher probabilities. Let $i^* = \argmax_i a_i$ be the highest accuracy forecaster, and let $a^* = a_{i^*}$.

\begin{definition}
  \label{accuracy_gap}
  The \textbf{accuracy gap} $\epsilon = a^* - \max_{i \neq i^*} a_i$ is the difference in accuracy of the first and second best forecasters.
\end{definition}

% For a given mechanism $M$ and $n$ forecasters with accuracy gap $\epsilon$, we let $m_\delta$ be the minimum number of events such that $M$ necessarily chooses $i^*$ with probability at least $1 - \delta$. 
Specifically, for any $m > m_\delta(M, n, \epsilon)$, $P(M(y, x) \neq i^*) \leq \delta$. $m_\delta$ gives us a measure of how many events are needed for a mechanism to stably pick the best forecaster. We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.

Similar to work in \cite{elf}, we will focus on using the proper scoring rule, the quadratic scoring rule in our forecaster selection mechanism.

\begin{definition}
  \label{scoring_rule}
  A \textbf{scoring rule}, $R$ is proper if $\forall p,y \in {0,1}, E_{x~p}[R(p,x)] \ge E_{x~p}[R(y,x)]$
\end{definition}

\begin{definition}
  \label{quadratic_scoring_rule}
  The \textbf{quadratic scoring rule}, is $R_q = 1 - (y - x)^2$, where $x$ denotes the observed outcome, and $y$ denotes the report.
\end{definition}

@@

\subsection{Truthfulness}
This mechanism is not truthful, as we can see with a few counterexamples. First, consider the case of a single event with $\theta = 0.9$, with $n = 2$. If both forecasters correctly report $0.9$, they will each with with probability $\frac{1}{2}$. However, if either of them deviates and reports some $y > 0.9$, they will win whenever $x = 1$. This happens with probability 0.9, so it increases their probability of winning. Therefore, this is an advantageous misreport, so $M_s$ is not truthful.

This extends to multiple events as well. If event 1 is the event given above, and for every subsequent event both forecasters report the same $y$, their overall score will be the same for all events but the first one, so that will determine the winner. Therefore, the untruthful forecaster will still have an advantage, so $M_s$ is not truthful for multiple events either.

@@

Let $F_{i, k}$ be the indicator function for forecaster $i$ winning the lottery for event $k$. Then, $F_i = \sum_k F_{i, k}$ is the random variable that is the number of events forecaster $i$ wins. The proof of Theorem 8 \cite{elf} utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance. However, this is not the case, and utilizing that fact gives an improvement in the lower bound. 
\begin{theorem}[Bernstein's Inequality]
  \label{bernstein}
  Given random variables $X_i$ for $1 \leq i \leq n$ such that $0 \leq X_i \leq 1$ almost surely, let $S = \sum_i X_i$. Then,
  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } ~.\]
\end{theorem}
\begin{theorem}
  \label{elf_bound}
    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$ ~.
    % For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
\end{theorem}
\emph{Proof:} Note that for any single event $k$, every forecaster wins with probability at best $\frac{2}{n}$, and at worst $\frac{1}{n} - \frac{1}{n(n-1)}$ (achieved when $y_i = 1$, $y_{j\neq i} = 0$, and $x_i = 1$). Since $F_{i, k}$ is just a binary random variable, it will have highest variance when it's expectation is as close to $\frac{1}{2}$ as possible. For nontrivially small $n$, this will mean its expectation is $\frac{2}{n}$ (or equivalently $P(F_{i, k} = 1) = \frac{2}{n}$), so its variance will be at most $\frac{2(n-2)}{n^2}$. So we have $\Var(F_{i, k}) \leq \frac{2(n-2)}{n^2} < \frac{2}{n}$.

@@

\begin{theorem}
  \label{elf_lower_bound}
    For $\delta < \frac{1}{2}$, $m_\delta(\elf, n, \epsilon) > n \log n$.
\end{theorem}
\emph{Proof:} Pick some $\delta < \frac{1}{2}$ and consider the case where $m = n \log n$ and $\theta_k = 1$ for every event. Let $y_{1, k} = 1$ and $y_{i, k} = 0$ for every $i > 1$. Therefore, forecaster 1 always forecasts correctly and has a quadratic score $R_q(1, 1) = 1$ for each event, while everyone else is wrong and has a quadratic score of $R_q(0, 1) = 0$ for each event. Then, $a_1 = 1$, and $a_i = 0$ for $i > 1$, so we have the worst possible accuracy gap $\epsilon = 1$.

@@

\begin{theorem}
  \label{shelf_truthful}
    $\shelf$ is truthful for $m \geq 1$ events.
\end{theorem}
\emph{Proof:} For each forecaster $j \in [1, n]$ fix forecaster's report.

@@

% \subsection{Truthfulness for multiple events}
\begin{theorem}
  \label{shelf_bound}
    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$.
\end{theorem}
\emph{Proof:} This proof is a slight modification of the proof of Theorem 8 in \cite{elf}.
